---
title: "Quantitative Analyses"
author: "Amanda D. Perez"
date: "December 01, 2016"
output: html_document
---
This script will conduct quantitative analyses with the data from the
Greater Good Science Center's Online Science of Happiness Course.

This is a huge dataset with nearly 200 variables. Many Q's could be looked at, but for
the purposed of this project I will narrow my scope.

This script will look at/answer the following questions:
1) Does the amount of time (weekly) spent on the course impact exam scores?
2) Do higher frequencies of doing happiness practices lead to higher exam scores?
3) What are the correlations b/w specific measures?
4) How do the various measures impact exam scores?
5) Are people who do a higher frequency of happiness practices happier?
6) Does paying for a verified certificate impact exam scores?

First, I will install/load the necessary libraries.
```{r eval=TRUE}
libs_needed <- c("Hmisc","stats")
install.packages(libs_needed)
lapply(libs_needed, require, character.only = TRUE)
```

Next, I will set my working directory and load the necessary file.
This file was created in the previous (01_merge-data.Rmd) file.
```{r eval=TRUE}
setwd("~/Desktop/ps239t_final/Data")
quant_data <- read.csv("Dataset_For_Quantitative_Analysis.csv")
```
objects(quant_data)
Question 1) Does the amount of time (weekly) spent on the course impact exam scores?
```{r eval=TRUE}
quant_data$Final <- (quant_data$Final)*100 #This is converting the exam score into a percent (out of 100%)
mod.1 <- lm(Final ~Weekly_Hours, data=quant_data ) #Running a linear regression
summary(mod.1)
```
Summary: Main effect of weekly hours spent on course such that the more time spent, the better students did on the final exam.

Question 2) Do higher frequencies of doing happiness practices lead to higher exam scores?
We will be looking at the 12 Happiness Practices taught throughout the course:
Frequency_3_Good_Things, Frequency_Active_Listening, Frequency_Awe_Walk, Frequency_Body_Scan, Frequency_Forgiveness, Frequency_Gratitude_Journal,
Frequency_Gratitude_Letter, Frequency_Ideal_Self, Frequency_Meditation, Frequency_Mindful_Breathing, Frequency_Random_Kindness, Frequency_Self_Compassion_Letter
```{r eval=TRUE}
mod.2 <- lm(Final ~ Frequency_3_Good_Things, data=quant_data)
summary(mod.2) #not significant

mod.3 <- lm(Final ~ Frequency_Active_Listening, data=quant_data)
summary(mod.3) #not significant

mod.4 <- lm(Final ~ Frequency_Awe_Walk, data=quant_data)
summary(mod.4)  #significant: more awe walks -> lower final exam scores. Counterintuitive finding.

mod.5 <- lm(Final ~ Frequency_Body_Scan, data=quant_data)
summary(mod.5) #not significant

mod.6 <- lm(Final ~ Frequency_Forgiveness, data=quant_data)
summary(mod.6) #significant: more foregiveness -> lower final exam scores. Counterintuitive finding.

mod.7 <- lm(Final ~ Frequency_Gratitude_Journal, data=quant_data)
summary(mod.7) #not significant

mod.8 <- lm(Final ~ Frequency_Gratitude_Letter, data=quant_data)
summary(mod.8) #significant: more gratitude letters -> lower final exam scores. Counterintuitive finding.

mod.9 <- lm(Final ~ Frequency_Ideal_Self, data=quant_data)
summary(mod.9) #significant: more ideal self practice-> lower final exam scores. Counterintuitive finding.

mod.10 <- lm(Final ~ Frequency_Meditation, data=quant_data)
summary(mod.10) #not significant

mod.11 <- lm(Final ~ Frequency_Mindful_Breathing, data=quant_data)
summary(mod.11) #higher mindfulness -> higher exam scores

mod.12 <- lm(Final ~ Frequency_Random_Kindness, data=quant_data)
summary(mod.12) #not significant

mod.13 <- lm(Final ~ Frequency_Self_Compassion_Letter, data=quant_data)
summary(mod.13) #significant: more compassion letters-> lower final exam scores. Counterintuitive finding.

mod.13b <- lm(Final ~ Frequency_3_Good_Things+Frequency_Active_Listening+ Frequency_Awe_Walk+ Frequency_Body_Scan+Frequency_Forgiveness+Frequency_Gratitude_Journal+
Frequency_Gratitude_Letter+ Frequency_Ideal_Self+Frequency_Meditation+Frequency_Mindful_Breathing+Frequency_Random_Kindness+ Frequency_Self_Compassion_Letter,data=quant_data)
summary(mod.13b)
```
Summary: Some counterintuitive findings, but when controlling for all of the practices, only mindfulness remained significant.
Higher frequency of mindfulness breathing led to higher final exam scores.


Question 3) What are the correlations b/w specific measures?
Specifically, we will look at Subjective happiness, sense of purpose, stress, and loneliness. 
```{r eval=TRUE}
measure.names <- c("LONELY" ,"SHS" ,"PURPOSE"  ,"STRESS") #names of variables I will subset
my.cors <- quant_data[measure.names] #creating a matrix w/complete observations &naming my variables
my.cors <- na.omit(my.cors)
names(my.cors) <- c("LONELY","SHS","PURPOSE","STRESS")
names(my.cors)
my.cors <- as.matrix(my.cors)
rcorr(my.cors, type="pearson") #RUNS CORRELATION MATRIX, ALL SIGNIFICANT

```
Summary: These correlations are all significant and all make sense. 
Loneliness is positively correlates with stress & negatively correlated with happiness & sense of purpose.
Happiness is positive correlated with sense of purpose & negatively w/stress & loneliness.



Question 4) How do the various measures impact exam scores?
Specifically looking at Loneliness, Happiness, Stress, and Purpose
```{r eval=TRUE}
mod.14 <- lm(Final ~ LONELY, data=quant_data)
summary(mod.14)#not significant

mod.15 <- lm(Final ~ SHS, data=quant_data)
summary(mod.15) #not significant

mod.16 <- lm(Final ~ STRESS, data=quant_data)
summary(mod.16) #significant: higher stress -> lower exam scores

mod.17 <- lm(Final ~ PURPOSE, data=quant_data)
summary(mod.17) #not significant

mod.17b <- lm(Final ~ PURPOSE+SHS+STRESS+LONELY,data=quant_data)
summary(mod.17b) #marginal
```
Summary: The more stressed a student is, the lower their final exam score is.

Question 5) Are people who do a higher frequency of happiness practices happier?
We will be looking at the 12 Happiness Practices taught throughout the course:
Frequency_3_Good_Things, Frequency_Active_Listening, Frequency_Awe_Walk, Frequency_Body_Scan, Frequency_Forgiveness, Frequency_Gratitude_Journal,
Frequency_Gratitude_Letter, Frequency_Ideal_Self, Frequency_Meditation, Frequency_Mindful_Breathing, Frequency_Random_Kindness, Frequency_Self_Compassion_Letter
```{r eval=TRUE}
mod.18 <- lm(SHS ~ Frequency_3_Good_Things, data=quant_data)
summary(mod.18) #significant & positive

mod.19 <- lm(SHS ~ Frequency_Active_Listening, data=quant_data)
summary(mod.19) #significant &positive

mod.20 <- lm(SHS ~ Frequency_Awe_Walk, data=quant_data)
summary(mod.20)  #significant & positive

mod.21 <- lm(SHS ~ Frequency_Body_Scan, data=quant_data)
summary(mod.21) #significant + positive

mod.22 <- lm(SHS ~ Frequency_Forgiveness, data=quant_data)
summary(mod.22) #significant & positive

mod.23 <- lm(SHS ~ Frequency_Gratitude_Journal, data=quant_data)
summary(mod.23) #significant & positive

mod.24 <- lm(SHS ~ Frequency_Gratitude_Letter, data=quant_data)
summary(mod.24) #significant & positive

mod.25 <- lm(SHS ~ Frequency_Ideal_Self, data=quant_data)
summary(mod.25) 

mod.26 <- lm(SHS ~ Frequency_Meditation, data=quant_data)
summary(mod.26) #significant & positive

mod.27 <- lm(SHS ~ Frequency_Mindful_Breathing, data=quant_data)
summary(mod.27) #significant & positive

mod.28 <- lm(SHS ~ Frequency_Random_Kindness, data=quant_data)
summary(mod.28) #significant & positive

mod.29 <- lm(SHS ~ Frequency_Self_Compassion_Letter, data=quant_data)
summary(mod.29) #significant & positive

mod.30 <- lm(SHS ~ Frequency_3_Good_Things+Frequency_Active_Listening+ Frequency_Awe_Walk+ Frequency_Body_Scan+Frequency_Forgiveness+Frequency_Gratitude_Journal+
Frequency_Gratitude_Letter+ Frequency_Ideal_Self+Frequency_Meditation+Frequency_Mindful_Breathing+Frequency_Random_Kindness+ Frequency_Self_Compassion_Letter,data=quant_data)
summary(mod.30)
```
Summary: 2 main effects persist after controlling for the other happiness practices.
Higher frequency of random acts of kindness -> higher subjective happiness
Higher frequency of ideal self practice -> higher subjective happiness


Question 6) Does paying for a verified certificate impact exam scores?
```{r eval=TRUE}
mod.31 <- lm(Final~ Enrollment.Track+Weekly_Hours, data=quant_data) #controlling for hours put into the course weekly
summary(mod.31)
```
Summary: Marginal main effect of hours spent (more hours -> higher exam scores) 
Main effect of track persisted after controlling for hours spent studying.
Having a paid certificate (verified track) -> higher exam scores versus students who audit.
