---
title: "04_sentiment_analysis"
author: "Amanda D. Perez"
date: "December 01, 2016"
output: html_document
---

This script will look at the polarity of text responses re: what
impact the science of happiness had on student's lives.
I will be breaking this down by enrollment track; This is based on the findings from the
quantitative analyses showing significant differences between the  groups.

First, I will install/load the necessary libraries.
```{r eval=TRUE}
require(ggplot2) # plotting discourse data
require(qdap) # quantiative discourse analysis of transcripts
require(data.table) # for easier data manipulation
require(scales) # to help us plot
```

Next, I will set my working directory and load the necessary file.
I will be using the same cleaned dataset used for previous analyses.
```{r eval=TRUE}
setwd("~/Desktop/ps239t_final/Data")
sentiment_data <- read.csv("Dataset_For_Quantitative_Analysis.csv")
```

In `qdap`, we analyze sentiment using the `polarity` function.
objects(sentiment_data)
```{r}
# calculate polarity
(poldat <- with(sentiment_data, polarity(Impact_TEXT, Enrollment.Track)))

# have a peak of each line
counts(poldat)[100:140,]

# plot
plot(poldat)

# we can get just the second plot this way:
x <- plot(poldat)
x$p2
```
Summary: There is a very slight difference in polarity of course impact statement based on course track.
Those on verified (paid) track have higher polarity. 

What about the impact of Weekly hours spent on course? Quanititative analyses also highlighted the importance.
```{r}
# calculate polarity
(poldat2 <- with(sentiment_data, polarity(Impact_TEXT, Weekly_Hours)))

# look at some of the lines
counts(poldat2)[100:140,]

```
Summary: It seems weekly hours put into the course also impacted polarity of impact statements.
Specifically, the higher polarity was given tho students who spent the most time on the course.