---
title: "05_visualizations"
author: "Amanda D. Perez"
date: "December 11, 2016"
output: html_document
---
This script will produce all of the necessary graphs.
First, I will install/load the necessary libraries.
```{r eval=TRUE}
libs_needed <- c("Hmisc","stats","ggplot2","grid","gridExtra","corrplot","wordcloud")
install.packages(libs_needed)
lapply(libs_needed, require, character.only = TRUE)
```

Next, I will set my working directory and load the necessary file.
quant_data was created in the first(01_merge-data.Rmd) file.

```{r eval=TRUE}
setwd("~/Desktop/ps239t_final/Data")
quant_data <- read.csv("Dataset_For_Quantitative_Analysis.csv")

```

Question 1) Does the amount of time (weekly) spent on the course impact exam scores?
Graph for Q1:
```{r eval=TRUE}
p <- ggplot(quant_data, aes(Weekly_Hours, Final)) + geom_point(size=1,position="jitter")+
  labs(title="Impact of Study Time on Exam Score") +
  labs(x="Weekly Hours Spent on Course", y="Final Exam Score %")+geom_smooth(method = "lm", se = TRUE)
grid.newpage()
footnote <- "\n\nNote: Each dot represents one student.\n The Y axis represents the % score on the Final Exam.\nThe blue line represents a fitted regression line and Standard Error."
g <- arrangeGrob(p, bottom = textGrob(footnote, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12)))
grid.draw(g)
#Slightly positive
```

Question 2) Do higher frequencies of doing happiness practices lead to higher exam scores?
We will be looking at the 12 Happiness Practices taught throughout the course:
Frequency_3_Good_Things, Frequency_Active_Listening, Frequency_Awe_Walk, Frequency_Body_Scan, Frequency_Forgiveness, Frequency_Gratitude_Journal,
Frequency_Gratitude_Letter, Frequency_Ideal_Self, Frequency_Meditation, Frequency_Mindful_Breathing, Frequency_Random_Kindness, Frequency_Self_Compassion_Letter

Q2 Graphs
```{r eval=TRUE}
p2 <- ggplot(quant_data, aes(Frequency_Mindful_Breathing, Final)) + geom_point(size=1,position="jitter")+
  labs(title="Impact of Mindful Breathing on Exam Scores") +
  labs(x="Frequency of Mindful Breathing throughout the course", y="Final Exam Score %")+geom_smooth(method = "lm", se = TRUE)
grid.newpage()
footnote2 <- "\n\nNote: Each dot represents one student.\n The Y axis represents the % score on the Final Exam.\nThe blue line represents a fitted regression line and Standard Error."
g2 <- arrangeGrob(p2, bottom = textGrob(footnote2, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12)))
grid.draw(g2)
#Slightly positive
```

Question 3) What are the correlations b/w specific measures?
Specifically, we will look at Subjective happiness, sense of purpose, stress, and loneliness. 
Q3 graph

```{r eval=TRUE}
measure.names <- c("LONELY" ,"SHS" ,"PURPOSE"  ,"STRESS") #names of variables I will subset
my.cors <- quant_data[measure.names] #creating a matrix w/complete observations &naming my variables
my.cors <- na.omit(my.cors)
names(my.cors) <- c("LONELY","SHS","PURPOSE","STRESS")
names(my.cors)
my.cors <- as.matrix(my.cors)
mcor <- cor(my.cors)
col <- colorRampPalette(c("#BB4444","#EE9988","#FFFFFF", "#77AADD", "#4477AA"))
corrplot(mcor, method="shade", shade.col=NA, tl.col="black", tl.srt=45,
         col=col(200), addCoef.col="black", addcolorlabel="no", order="AOE", type="lower",title="\nCorrelation Matrix of Loneliness, Stress, Happiness, and Sense of Purpose")
#Blue = positive correlation
#Red = negative correlation
#All are significant

```

Question 4) How do the various measures impact exam scores?
Specifically looking at Loneliness, Happiness, Stress, and Purpose
Q4 Graphs
```{r eval = TRUE}

p3 <- ggplot(quant_data, aes(STRESS, Final)) + geom_point(size=1,position="jitter")+
  labs(title="Impact of Stress on Exam Scores") +
  labs(x="Stress", y="Final Exam Score %")+geom_smooth(method = "lm", se = TRUE)
grid.newpage()
footnote3 <- "\n\nNote: Each dot represents one student.\n The Y axis represents the % score on the Final Exam.\nThe blue line represents a fitted regression line and Standard Error."
g3 <- arrangeGrob(p3, bottom = textGrob(footnote3, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12)))
grid.draw(g3)
#slightly negative

```

Question 5) Are people who do a higher frequency of happiness practices happier?
We will be looking at the 12 Happiness Practices taught throughout the course:
Frequency_3_Good_Things, Frequency_Active_Listening, Frequency_Awe_Walk, Frequency_Body_Scan, Frequency_Forgiveness, Frequency_Gratitude_Journal,
Frequency_Gratitude_Letter, Frequency_Ideal_Self, Frequency_Meditation, Frequency_Mindful_Breathing, Frequency_Random_Kindness, Frequency_Self_Compassion_Letter

Q5 Graphs
```{r eval=TRUE}

p4 <- ggplot(quant_data, aes(Frequency_Ideal_Self , SHS)) + geom_point(size=1,position="jitter")+
  labs(title="Impact of Frequency of Ideal Self Happines Practice on Subjective Happiness") +
  labs(x="Frequency of doing Ideal Self Practice", y="Subjective Happiness")+geom_smooth(method = "lm", se = TRUE)
grid.newpage()
footnote4 <- "\n\nNote: Each dot represents one student.\n The Y axis represents Subjective Happiness.\nThe blue line represents a fitted regression line and Standard Error."
g4 <- arrangeGrob(p4, bottom = textGrob(footnote4, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12)))
grid.draw(g4)
#positive relationship

p5 <- ggplot(quant_data, aes(Frequency_Random_Kindness, SHS)) + geom_point(size=1,position="jitter")+
  labs(title="Impact of Frequency of Random acts of Kindness Happiness Practice of Subjective Happiness") +
  labs(x="Frequency of doing Random Acts of Kindness", y="Subjective Happiness")+geom_smooth(method = "lm", se = TRUE)
grid.newpage()
footnote5 <- "\n\nNote: Each dot represents one student.\n The Y axis represents Subjective Happiness.\nThe blue line represents a fitted regression line and Standard Error."
g5 <- arrangeGrob(p5, bottom = textGrob(footnote5, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12)))
grid.draw(g5)
#positive relationship
```

Question 6) Does paying for a verified certificate impact exam scores?
Graphing Q6
```{r eval=TRUE}
p6 <- ggplot(quant_data, aes(Enrollment.Track))+stat_summary_bin(aes(y = Final), fun.y = "mean", geom = "bar", fill="blue")+
labs(title="Impact of Auditing vs. Paid Certificate on Final Exam Score") +
  labs(x="Course Track", y="Final Exam Score %")
grid.newpage()
grid.draw(p6)
#verified (paid) track -> higher exam scores
```

Creating a bar plot of most frequent words & word cloud of the text responses for
what students liked the most about the course.
```{r}
docs <- Corpus(VectorSource(quant_data$Course_Like_Most_TEXT))
dtm <- DocumentTermMatrix(docs,
           control = list(tolower = TRUE,
                          removePunctuation = TRUE,
                          removeNumbers = TRUE,
                          stopwords = TRUE,
                          stemming=TRUE))
freq <- sort(colSums(as.matrix(dtm)),decreasing=TRUE)
head(freq)

wf <- data.frame(word=names(freq), freq=freq)
head(wf)

p7 <- subset(wf, freq>50) %>%
   ggplot(aes(word, freq)) +
        geom_bar (stat ="identity") +
        theme(axis.text.x=element_text(angle=45,hjust=1))+
  labs(title="Most Frequent Words in Text for What Students Liked Most") +
  labs(x="Words", y="Frequency")
grid.newpage()
grid.draw(p7)

# wordcloud
set.seed(123)
plot.new()
wordcloud(names(freq), freq, max.words=100, colors=brewer.pal(6,"Dark2"))+
text(x=0.5, y=0.99, "Word Cloud of What Students Liked Most")


```
Summary: The most frequent words illuminate that the students
enjoy the course vidoes & the happiness practices.
The word cloud highlights that common words were: happiness practices, videos, scientific research, and the course instructors (dacher keltner & Emiliana!)

Creating a bar plot of most frequent words & word cloud of the text responses for
what suggestions were given for course improvement.
```{r}
docs2 <- Corpus(VectorSource(quant_data$Course_Changes_TEXT))
dtm2 <- DocumentTermMatrix(docs2,
           control = list(tolower = TRUE,
                          removePunctuation = TRUE,
                          removeNumbers = TRUE,
                          stopwords = TRUE,
                          stemming=TRUE))
freq2 <- sort(colSums(as.matrix(dtm2)),decreasing=TRUE)
head(freq2)

wf2 <- data.frame(word=names(freq2), freq2=freq2)
head(wf2)

p8 <- subset(wf2, freq2>50) %>%
    ggplot(aes(word, freq2)) +
        geom_bar (stat ="identity") +
        theme(axis.text.x=element_text(angle=45,hjust=1))+
   labs(title="Most Frequent Words in Text for Course Improvements") +
  labs(x="Words", y="Frequency")
grid.newpage()
grid.draw(p8)
# wordcloud
set.seed(123)
wordcloud(names(freq2), freq2, max.words=100, colors=brewer.pal(6,"Dark2"))+
text(x=0.5, y=0.99, "Word Cloud of Suggestions for Improvement")
```
Summary: The most frequent words illuminate that the students may be feeling that the course takes up too much time to finish.
The word cloud highlights the same idea, time & week are prominent in the cloud. This could be that maybe there is not enough time (9 weeks)
to finish all of the course content. Perhaps they do not like the weekly style of the course either. 

The following graph will plot the polarity of the statement of how the course impacted the student's lives. It will take into account which track they are on.
```{r}
# calculate polarity
poldat <- with(quant_data, polarity(Impact_TEXT, Enrollment.Track))
p9 <- plot(poldat)
p9 <- x$p2
grid.newpage()
footnote9 <- "\n\nNote: This graph shows the polarity of the student's statement of how the course.\nimpacted them. It also takes into acount which track they are on."
g9 <- arrangeGrob(p9, bottom = textGrob(footnote9, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12)))
grid.draw(g9)
```
Summary: There is a slight difference between the two enrollment tracks.


The following graph will plot the polarity of the statement of how the course impacted the student's lives. It will take into account
how many hours per week students spent on the course.
```{r}
# calculate polarity
poldat2 <- with(quant_data, polarity(Impact_TEXT, Weekly_Hours))
x2 <- plot(poldat2)
p10 <- x2$p2
grid.newpage()
footnote10 <- "\n\nNote: This graph shows the polarity of the student's statement of suggestions for course improvements\nIt also takes into acount how many hours a week they put into the course."
g10<- arrangeGrob(p10, bottom = textGrob(footnote10, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12)))
grid.draw(g10)
```
Summary: The highest polarity ratings of course impact came from those who spent the most amount of time on the course.

Now I will save all of my plots as individual PDFs

```{r}
setwd("~/Desktop/ps239t_final/Results") #setting my working directory to the results folder.
pdf("time_exams.pdf")
grid.draw(g)
dev.off()

pdf("mindful_breathing_exams.pdf")
grid.draw(g2)
dev.off()

pdf("stress_exams.pdf")
grid.draw(g3)
dev.off()

pdf("ideal_self_happiness.pdf")
grid.draw(g4)
dev.off()

pdf("random_kindness_happiness.pdf")
grid.draw(g5)
dev.off()

pdf("verified_track_exams.pdf")
grid.draw(p6)
dev.off()

pdf("frequency_liked_most.pdf")
grid.draw(p7)
dev.off()

pdf("word_cloud_liked_most.pdf")
wordcloud(names(freq), freq, max.words=100, colors=brewer.pal(6,"Dark2"))+
text(x=0.5, y=0.99, "Word Cloud of What Students Liked Most")
dev.off()

pdf("frequency_suggestions.pdf")
grid.draw(p8)
dev.off()

pdf("word_cloud_suggestions.pdf")
wordcloud(names(freq2), freq2, max.words=100, colors=brewer.pal(6,"Dark2"))+
text(x=0.5, y=0.99, "Word Cloud of Suggestions for Improvement")
dev.off()

pdf("verified_track_course_impact.pdf")
grid.draw(g9)
dev.off()

pdf("hours_spent_course_impact.pdf")
grid.draw(g10)
dev.off()

pdf("Correlation_Matrix.pdf")
col <- colorRampPalette(c("#BB4444","#EE9988","#FFFFFF", "#77AADD", "#4477AA"))
corrplot(mcor, method="shade", shade.col=NA, tl.col="black", tl.srt=45,
         col=col(200), addCoef.col="black", addcolorlabel="no", order="AOE", type="lower",title="\nCorrelation Matrix of Loneliness, Stress, Happiness, and Sense of Purpose")
dev.off()
```

